Supplemental Materials for: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-15 MS/supp.Rmd
updating ignore file, and fixing some stuff in supp

Before embarking on the case studies readers will need to load the necessary R packages.

```{r loadpackages, echo = TRUE, results = "hide", messages = FALSE, class.source='klippy'}
#install.packages("pacman")
pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr, Rcpp)
devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE)
```

@@

@@

In some cases, CTmax was measured twice on the same cohort of animals (e.g. using a different endpoint), which generates a source of non-independence between effect sizes. We can account for this source of non-independence by correlating errors between dependent effect sizes. The `make_VCV_matrix` from `metaAidR` is a handy function to perform this correction, and assume a correlation of r = 0.5 by default. We termed the created variance-covariance matrix as `VCV_ARR`.

@@

```{r class.source='klippy'}
# Download the data file from OSF
osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download(conflicts = "overwrite")

>>>>

Before embarking on the case studies readers will need to load the necessary R packages. Note that the first two lines are commented out. If you don't have these packages, just install these by removing the `#`.

```{r loadpackages, echo = TRUE, results = "hide", messages = FALSE, class.source='klippy'}
#install.packages("pacman")
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE)
pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr)
```

@@

### Calculate Effect Size

@@

In some cases, CTmax was measured twice on the same cohort of animals (e.g. using a different endpoint), which generates a source of non-independence between effect sizes. We can account for this source of non-independence by correlating errors between dependent effect sizes. The `make_VCV_matrix` from [`metaAidR`](https://github.com/daniel1noble/metaAidR) is a handy function to perform this correction, and assume a correlation of r = 0.5 by default. We termed the created variance-covariance matrix `VCV_ARR`.

@@

```{r class.source='klippy'}
# Download the data file from OSF
osfr::osf_retrieve_file("https://osf.io/zubky/") %>% osfr::osf_download(conflicts = "overwrite")
